Meta RL analyses

### 2019-05-01 meta_RL_analyses.Rmd
TSNE!

summary_plot = function(data,  x_var, y_var, color_var, optimal_baseline_data=NULL, other_baseline_data=NULL, palette="Set2") {

@@

@@

@@

# embeddings

```{r}
for (result_subdir in result_subdirs) {
  for (emb_type in c("guess", "final")) {
    emb_d = data.frame()
    for (run_i in 0:(num_runs-1)) {
      filename = sprintf("%s%s/run%i_%s_embeddings.csv", results_dir, result_subdir, run_i, emb_type)
      if (!file.exists(filename)) {
        next
      }
      this_d = read.csv(filename, header=T)
      this_d$run = run_i
      emb_d = bind_rows(emb_d, this_d)
    }

    pcs = prcomp(emb_d %>% select(-dimension, -run, -starts_with("is"), -starts_with("toggle")), center=T, scale=T)
    pc_d = data.frame(pcs$rotation)
    pc_d$task = row.names(pc_d)
    ggplot(pc_d, aes(x=PC1, y=PC2, color=task)) +
      geom_point() +
      geom_text(aes(label=task)) +
      guides(color=F)
    ggsave(sprintf("plots/%s_PCA_basic_%s.png", result_subdir, emb_type), width=7, height=7)

    pcs = prcomp(emb_d %>% select(-dimension, -run), center=T, scale=T)
    pc_d = data.frame(pcs$rotation)
    pc_d$task = row.names(pc_d)
    ggplot(pc_d, aes(x=PC1, y=PC2, color=task)) +
      geom_point() +
      geom_text(aes(label=task)) +
      guides(color=F)
    ggsave(sprintf("plots/%s_PCA_full_%s.png", result_subdir, emb_type), width=7, height=7)
  }
}
```

>>>>

summary_plot = function(data,  x_var, y_var, color_var, optimal_baseline_data=NULL, other_baseline_data=NULL, palette="Set2", continuous_x=F) {

@@

  if (continuous_x) {
    p = p + 
      geom_line(stat="summary", fun.y=mean, size=2) 
  }

@@

```{r}
summary_plot(reward_d %>%
               filter(run_type %in% c("basic", "basic_random_holdout_longer", "meta_batch_128", "language_simplified_random_holdout")),
             "epoch", "reward", "is_new_game",
             continuous_x=T) +
  facet_wrap(. ~ named_run_type) +
  geom_smooth(method="lm")

#ggsave("writing/figures/basic_meta_learning_integrating_over_time.png", width=4.2, height=3)
```

@@

# embeddings
```{r}
library(tsne)
```

```{r}
#for (result_subdir in result_subdirs) {
#  for (emb_type in c("guess", "final")) {
for (result_subdir in c("basic")) {
  for (emb_type in c("final")) {
    emb_d = data.frame()
    for (run_i in 0:(num_runs-1)) {
      filename = sprintf("%s%s/run%i_%s_embeddings.csv", results_dir, result_subdir, run_i, emb_type)
      if (!file.exists(filename)) {
        next
      }
      this_d = read.csv(filename, header=T)
      this_d$run = run_i
      emb_d = bind_rows(emb_d, this_d)
    }

    set.seed(0) # reproducible tsne
    pcs = prcomp(emb_d %>% select(-dimension, -run, -starts_with("is"), -starts_with("toggle")), center=T, scale=T)
    pc_d = data.frame(pcs$rotation)
    pc_d$task = row.names(pc_d)
    pc_d = pc_d %>% 
      mutate(game_type = str_extract(task, "high_card|match|straight_flush|pairs_and_high|sum_under"),
             losers = grepl("l_1", task),
             black_valuable = grepl("bv_1", task),
             suits_rule = grepl("sr_1", task),
             named_game_type = name_game_type(game_type))
    ggplot(pc_d, aes(x=PC1, y=PC2, shape=named_game_type, color=losers, size=black_valuable)) +
      geom_point() +
      scale_color_brewer(palette="Dark2") + 
      labs(x="Dimension 1", y="Dimension 2") +
      guides(size=guide_legend(title="Switch suits"),
             shape=guide_legend(title="Game"),
             color=guide_legend(title="Losers"))
    ggsave(sprintf("plots/%s_PCA_basic_%s.png", result_subdir, emb_type), width=7, height=7)

    ts = data.frame(tsne(emb_d %>% select(-dimension, -run, -starts_with("is"), -starts_with("toggle")) %>% as.matrix() %>% t(),
                         perplexity=5,
                         initial_dims=10))
    ts$task = pc_d$task
    ts = ts %>% 
      mutate(game_type = str_extract(task, "high_card|match|straight_flush|pairs_and_high|sum_under"),
             losers = grepl("l_1", task),
             black_valuable = grepl("bv_1", task),
             suits_rule = grepl("sr_1", task),
             named_game_type = name_game_type(game_type))
    ggplot(ts, aes(x=X1, y=X2, shape=named_game_type, color=losers, size=black_valuable)) +
      geom_point() + 
      scale_color_brewer(palette="Dark2") + 
      labs(x="Dimension 1", y="Dimension 2") +
      guides(size=guide_legend(title="Switch suits"),
             shape=guide_legend(title="Game"),
             color=guide_legend(title="Losers"))
    ggsave(sprintf("plots/%s_tsne_basic_%s.png", result_subdir, emb_type), width=7, height=7)

    set.seed(0) # reproducible tsne
    pcs = prcomp(emb_d %>% select(-dimension, -run, -contains("suits_rule")), center=T, scale=T)
    pc_d = data.frame(pcs$rotation)
    pc_d$task = row.names(pc_d)
    ggplot(pc_d, aes(x=PC1, y=PC2, color=task)) +
      geom_point() +
      geom_text(aes(label=task)) +
      guides(color=F)
    ggsave(sprintf("plots/%s_PCA_full_%s.png", result_subdir, emb_type), width=7, height=7)

    ts = data.frame(tsne(emb_d %>% select(-dimension, -run, -contains("suits_rule")) %>% as.matrix() %>% t(),
                         perplexity=5,
                         initial_dims=10))
    ts$task = row.names(pc_d)
    ts = ts %>%
      mutate(is_meta = grepl("is_|toggle_", task),
             meta_type = ifelse(is_meta, str_extract(task, "toggle|is"), NA),
             game_type = str_extract(task, "high_card|match|straight_flush|pairs_and_high|sum_under"),
             losers = grepl("l_1", task),
             black_valuable = grepl("bv_1", task),
             suits_rule = grepl("sr_1", task),
             named_game_type = name_game_type(game_type),
             type_var = ifelse(is_meta, task, "basic"),
             type_var = factor(type_var,
                               levels=c('basic', 'is_high_card', 'is_straight_flush', 'is_match', 'is_pairs_and_high', 'is_sum_under', 'is_suits_rule', 'is_losers', 'is_black_valuable', 'toggle_suits_rule', 'toggle_losers', 'toggle_black_valuable'),
                               labels=c('Basic', 'is_high_card', 'is_poker', 'is_match', 'is_pairs', 'is_blackjack', 'is_suits_rule', 'is_losers', 'is_switched_suits', 'toggle_suits_rule', 'toggle_losers', 'toggle_switch_suits'))
             )
    ggplot(ts, aes(x=X1, y=X2, color=type_var, alpha=is_meta)) +
      geom_point() +
      geom_text(data=ts %>% filter(is_meta),
                aes(label=type_var),
                position=position_nudge(y=40, x=-100),
                size=4) +
      scale_alpha_manual(values=c(0.33, 1)) + 
      scale_color_brewer(palette="Set3") + 
      labs(x="Dimension 1", y="Dimension 2") +
      guides(alpha=F,
             color=guide_legend(title="Task"))
    ggsave(sprintf("plots/%s_tsne_full_%s.png", result_subdir, emb_type), width=7, height=6)
  }
}
```
